 Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings

### 2020-09-18 paper.Rmd
rejig output

---
title: " Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings"
author:
  - name: Stuart Lee
  - name: Di Cook
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: false
    number_sections: no
bibliography: liminal.bib
---
```{r setup-videos, cache = FALSE}
vid_lookup <- tibble::tribble(
  ~key, ~url, ~path,
  "gaussian",  "https://player.vimeo.com/video/439635921", here::here("img", "liminal-screenshot-gaussian.png"),
  "hierarchical", "https://player.vimeo.com/video/439635905", here::here("img", "liminal-screenshot-hierarchical.png"),
  "trees-01", "https://player.vimeo.com/video/439635892", here::here("img", "liminal-screenshot-trees-01.png"),
  "trees-02", "https://player.vimeo.com/video/439635863", here::here("img", "liminal-screenshot-trees-02.png"),
  "mouse-01", "https://player.vimeo.com/video/439635812", here::here("img", "liminal-screenshot-mouse-01.png"),
  "mouse-02", "https://player.vimeo.com/video/439635843", here::here("img", "liminal-screenshot-mouse-02.png")
)

>>>>

---
title: " Casting multiple shadows: high-dimensional interactive data visualisation with tours and embeddings"
author:
  - name: Stuart Lee
  - name: Di Cook
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: false
    number_sections: no
bibliography: liminal.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r setup-videos, cache = FALSE, echo = FALSE}
vid_lookup <- tibble::tribble(
  ~key, ~url, ~path,
  "gaussian",  "https://player.vimeo.com/video/439635921", here::here("img", "liminal-screenshot-gaussian.png"),
  "hierarchical", "https://player.vimeo.com/video/439635905", here::here("img", "liminal-screenshot-hierarchical.png"),
  "trees-01", "https://player.vimeo.com/video/439635892", here::here("img", "liminal-screenshot-trees-01.png"),
  "trees-02", "https://player.vimeo.com/video/439635863", here::here("img", "liminal-screenshot-trees-02.png"),
  "mouse-01", "https://player.vimeo.com/video/439635812", here::here("img", "liminal-screenshot-mouse-01.png"),
  "mouse-02", "https://player.vimeo.com/video/439635843", here::here("img", "liminal-screenshot-mouse-02.png")
)
